Output Summary

### 2020-10-20 03-post-process/output-plots.Rmd
Add smolt-to-adult return rate plot

>>>>

# Smolt-to-Adult Rates

This is survival from $Mb$ (smolts in tributary, prior to mortality associated with movement to LGD) to $Ra$ (adults returning to tributary, vulnerable to being counted at weir).

The adult part is calculated across return years, by summing the number of adults of each age (regardless of sex) that return in the appropriate years. For example, the SAR for brood year 1991 uses smolt that were spawned in 1991, out-migrated in spring 1993, divided by the sum of age 3 adults in 1994, age 4 adults in 1995, and age 5 adults in 1996. The calculation is done for hatchery and natural origin fish separately. Only SARs through brood year 2014 are calculated, since this is the last year of complete adult returns.

Other SARS could be calculated, but currently this is the only one that is comparable between hatchery and natural origins.

```{r}
# function to calculate posterior 
get_SAR_post = function(post, jags_data) {
  # extract posterior abundances
  Ra_post = post_subset(post, "^Ra[", T) # adults returning to tributary
  Mb_post = post_subset(post, "^Mb[", T) # smolts leaving tributary in spring

  # number of saved samples
  ni = post_dim(post, "saved")

  # first and last brood year SAR can be calculated for
  first_SAR_y = jags_data$kmax + 1
  last_SAR_y = jags_data$ny - jags_data$kmax

  # containers
  nat_SAR = hat_SAR = NULL

  # loop over mcmc iters
  for (i in 1:ni) {
    # extract quantities for this iter
    Ra = array_format(Ra_post[i,])
    Mb = array_format(Mb_post[i,])

    # give names
    dimnames(Ra) = dimnames(jags_data$p_remove)
    dimnames(Mb) = dimnames(jags_data$Mb_obs)

    # drop sex structure from Ra
    Ra = Ra[,,1,] + Ra[,,2,]

    # loop over years
    nat_SAR_i = hat_SAR_i = NULL
    for (y in first_SAR_y:last_SAR_y) {
      # sum up smolts across life history types
      nat_smolt = sum(Mb[y,,"Nat"])
      hat_smolt = sum(Mb[y,,"Hat"], na.rm = T)

      # sum up returing adults from this brood
      nat_adults = Ra[y+3,1,"Nat"] + Ra[y+4,2,"Nat"] + Ra[y+5,3,"Nat"]
      hat_adults = Ra[y+3,1,"Hat"] + Ra[y+4,2,"Hat"] + Ra[y+5,3,"Hat"]

      nat_SAR_i = c(nat_SAR_i, nat_adults/nat_smolt)
      hat_SAR_i = c(hat_SAR_i, hat_adults/hat_smolt)
    }

    # combine with other mcmc iters
    nat_SAR = rbind(nat_SAR, nat_SAR_i)
    hat_SAR = rbind(hat_SAR, hat_SAR_i)
  }

  colnames(nat_SAR) = paste0("SAR[", first_SAR_y:last_SAR_y, ",1]")
  colnames(hat_SAR) = paste0("SAR[", first_SAR_y:last_SAR_y, ",2]")

  # drop out SAR years for hatchery fish where missing
  hat_SAR = hat_SAR[,!is.na(colSums(hat_SAR))]

  out = cbind(nat_SAR, hat_SAR)
  return(out)
}

# apply the function
SAR_post = get_SAR_post(post, jags_data)

# combine samples with main posterior object
post = post_bind(post, SAR_post)

# calculate/format posterior summaries
SAR_mean = array_format(post_summ(post, "SAR")["mean",]) * 100
SAR_lwr = array_format(post_summ(post, "SAR")["2.5%",]) * 100
SAR_upr = array_format(post_summ(post, "SAR")["97.5%",]) * 100

# subset years
all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])
SAR_yrs = all_yrs[1:nrow(SAR_mean)]

# graphics device
par(mar = c(3,3,1,1), mgp = c(2,0.35,0), tcl = -0.2)

# blank plot with appropriate dimensions
plot(SAR_mean[,1] ~ SAR_yrs, ylab = "Adults/100 Smolt", xlab = "Brood Year",
     xlim = range(all_yrs), ylim = c(0, max(SAR_upr, na.rm = T)), type = "n", las = 1)

# draw posterior summary for natural origin
polygon(x = c(SAR_yrs, rev(SAR_yrs)), y = c(SAR_lwr[,1], rev(SAR_upr[,1])), col = alpha("skyblue2", 0.5), border = NA)
lines(SAR_lwr[,1] ~ SAR_yrs, col = "blue", lty = 2)
lines(SAR_upr[,1] ~ SAR_yrs, col = "blue", lty = 2)
lines(SAR_mean[,1] ~ SAR_yrs, col = "blue", lwd = 2)

# draw posterior summary for hatchery origin
polygon(x = c(SAR_yrs, rev(SAR_yrs)), y = c(SAR_lwr[,2], rev(SAR_upr[,2])), col = alpha("salmon", 0.5), border = NA)
lines(SAR_lwr[,2] ~ SAR_yrs, col = "red", lty = 2)
lines(SAR_upr[,2] ~ SAR_yrs, col = "red", lty = 2)
lines(SAR_mean[,2] ~ SAR_yrs, col = "red", lwd = 2)

# draw a legend
legend("topright", legend = c("Natural", "Hatchery"), title = "Origin",
       pch = 22, col = c("blue", "red"), pt.cex = 2, pt.bg = alpha(c("skyblue2", "salmon"), 0.5), bty = "n")
```
